### 2012-12-07 doc/description.tex
database modules refactoring

>>>>

\subsection{Database Schema Model}
The database schema model is defined by following concepts:
\begin{itemize}
	\item Table : table represents a basic concept of database schema. It has a unique name, one or more column and it can be related to other tables in the schema by foreign keys. Rows in the table represents stored data.
	\item Column : columns define possible data values and types which can be part of a table record.
	\item Foreign key :
	\item Primary key :
	\item Db-Type : represents primitive types in the database. There are usually defined types such as Char, Integer, Boolean etc. There is only one type defined in the model which is called DB-STRING.
	\item Constraint : there are two types of constraints defined in the model. Both constraints are column constraints - first constraint defines unique records in a column, second constraint defines non-empty columns.
\end{itemize}
